---
title: "learnggplot"
author: "Muthia"
date: "7/28/2020"
output: html_document
---
```{r}
covid <- read.csv("C:/Users/Aulia Muthia/Downloads/Algoritma/covidRT/covidRT/data_input/covid_clean.csv")
covid <- covid [,2:6]
covid$date <- as.Date (covid$date)

# order based on covid$date
covid <- covid[order(covid$date),]
head(covid)
```

# You are assigned by WHO to study the cases in the North America continent / region
# Give the new dataframe the name "northam"

```{r}
northam <- subset (covid, country == "US" | country == "Canada")
summary(northam)
```
```{r}
plot(x=northam$date, 
     y=log(northam$confirmed) , 
     type = "l", 
     )
```

# You are assigned by WHO to study the cases in the key Europe countries ("Germany", Italy, Spain,France, "United Kingdom" )
# Give the new dataframe the name "euro5"

```{r}
euro5 <- subset (covid, 
                   country == "Germany" |
                    country == "Italy" | 
                    country == "Spain" |
                     country == "France" |
                     country == "United Kingdom")
summary(euro5)
```

Challange : In my ggplot I want all 5 countries + Indonesia + Canada


```{r}
euro5countries <- c("Germany", "Italy", "Spain","France" , "United Kingdom" )
euro5 <- subset (covid, country %in% euro5countries)
head(euro5)

```

```{r}
usa <- subset (covid, country=="US")
ggplot (usa, 
        mapping = aes(x=date ,
                      y= confirmed,
                      color =country))+geom_line()
```


#In my ggplot I want all 5 countries + Indonesia + Canada

```{r}
targetcountries <- c("Germany", "Italy", "Spain","France" , "United Kingdom", "Indonesia", "Canada" )
target <- subset (covid,country%in%targetcountries)
plot1 <- ggplot (target, mapping = aes(x=date, y=deaths, color=country)) 
plot1 +geom_line()
```

```{r}
#Option 1
plot1 + geom_line() + geom_point (col="black", size=0.5)

#Option 2
plot1 + geom_line(size=2) + geom_point (col="black", size=0.5)

#Option 3
plot1 + geom_boxplot() 
```

```{r}
#geom boxplot dan geom jitter itu layering sistem jadi yang duluan itu yang dibawah
#buat warna naronya di geom semua, karna yang di mapping bener2 hanya mapping data aja
ggplot (data=target, mapping=aes(x=country,y=recovered,fill=country)) +geom_jitter() +
  geom_boxplot() +
  labs (x="Country", 
        y="Healed" , 
        title = "COVID-19 Path to Recovery", 
        subtitle = "Germany leading in COVID-19 Recovery", 
        caption = "Developed by : Muthi, Strategic Performance Team") + 
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank()
  ) 
#https://github.com/Argaadya/tidytuesday
#https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ04-charting-with-tidyquant.html
#https://github.com/onlyphantom/ggplot2cheatsheet

```

```{r}
ggplot(data = covid[covid$confirmed > 20000,],
       aes(x=deaths)) +
  geom_histogram(binwidth = 1000, fill="seagreen") +
  geom_freqpoly(binwidth = 1000, col="hotpink")
```

```{r}
covid[order(covid$confirmed,decreasing=TRUE),]
```

# You can also search on #TidyTuesday on twitter. They put new data every week for you to practice your data visualization. Some people there share their code if you wish to copy


29 August 2020 (day 3)

Practice Create a df name newdata by subsetting covid to take rows where confirmed cases are above 10000 (on the most recent data)
1. look only at most recent day
2. filter for countries with more than 10000

```{r}
#data[row_condition, col_condition]
n <- 10000
newdata <- subset(mostrecent, 
                  confirmed > n & 
                    date == max(date))
head(newdata)
```

As of the latest information, r nrow(newdata) countries have more than 10000 cases

We refer to the stage of 'newdata' as being "wide", not a "tall" data
```{r}
dim(newdata)
```

Melt melts the data from wide to tall // similar with pivoting // #id means that this is the primary key // In this case, all the date are the same
```{r}
melted <- melt(newdata [,2:5], id="country")
tail(melted)
```

```{r}
plot <- ggplot(melted, 
               aes(x=country,y=value/1000,fill=variable)) + 
  geom_col(position = "stack") +
  labs (y="(in thousands)",
        title = "COVID - 19 Pandemic, 2020",
        subtitle = "Data source from JHU CSSE",
        caption = "Developed by : Muthi, Strategic Performance Team") + 
  #flip x to y and y to x 
  coord_flip() +
  theme_clean() +
  theme (
    legend.position = "left",
    axis.text.x = element_text(angle=90,hjust=1),
    panel.grid.major.x=element_blank(),
    title = element_text(face="bold")
  ) 
plot

#https://github.com/onlyphantom/safeskies
#https://www.quora.com/profile/Samuel-Chan-3
#https://github.com/onlyphantom/rgraphics

```
